Nitrogen cycling in the CLM5: controls on responses to environmental forcing

### 2018-11-13 figures.tex

 \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_STATE_1CLM50defpft_trans_1x1pt_US-Me2_ens_MIC_y1.png}
     \caption{Response of control model states and fluxes to parameter perturbation across -1 to +1 range of parameter variation at Metolius Forest State}
     \label{MET state}
  \end{figure}

 \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_STATE_1CLM50defpft_trans_1x1pt_US-NR1_ens_MIC_y1_2012.png}
     \caption{Niwot Forest State}
     \label{NR1 state}
  \end{figure}

   \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_STATE_1CLM50defpft_trans_1x1pt_US_Ha1_ens_MIC_y1_2012.png}
     \caption{Harvard Forest State}
     \label{HVF state}
  \end{figure}

 \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_FERT_1CLM50defpft_ndep_1x1pt_US_Ha1_ens_MIC_p1_2012.png}
     \caption{Harvard Forest Nitrogen Fertilization}
     \label{HRV ndep}
  \end{figure}

   \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_FERT_1CLM50defpft_celev_1x1pt_US_Ha1_ens_MIC_p1_2012.png}
     \caption{Harvard Forest CO2 Fertilization}
     \label{HRV celev}
  \end{figure}

   \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_FERT_1CLM50defpft_ndep_1x1pt_Br-cax_ens_MIC_p1_2012.png}
     \caption{Caxiuana Forest Nitrogen Fertilization}
     \label{CAX ndep}
  \end{figure}

   \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_FERT_1CLM50defpft_celev_1x1pt_Br-cax_ens_MIC_p1_2012.png}
     \caption{Caxiuana Forest CO2 Fertilization}
     \label{CAX celev}
  \end{figure}

   \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth,left]{matlab/figures/NOVc_FERT_1CLM50defpft_ndep_1x1pt_US-Me2_ens_MIC_p1_2012.png}
     \caption{Metolius Forest Nitrogen Fertilization}
     \label{MET ndep}
  \end{figure}

   \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_FERT_1CLM50defpft_celev_1x1pt_US-Me2_ens_MIC_p1_2012.png}
     \caption{Metolius Forest CO2 Fertilization}
     \label{MET celev}
  \end{figure}

   \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_FERT_1CLM50defpft_ndep_1x1pt_US-NR1_ens_MIC_p1_2012.png}
     \caption{Niwot Forest Nitrogen Fertilization}
     \label{NR1 ndep}
  \end{figure}

   \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_FERT_1CLM50defpft_celev_1x1pt_US-NR1_ens_MIC_p1_2012.png}
     \caption{Niwot Forest CO2 Fertilization}
     \label{NR1 celev}
  \end{figure}

>>>>

 \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_STATE_1CLM50defpft_trans_1x1pt_US-Me2_ens_MIC_y1.png}
     \caption{Response of control model states and fluxes to parameter perturbation across -1 to +1 range of parameter variation at Metolius Forest}
     \label{MET state}
  \end{figure}

 \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_STATE_1CLM50defpft_trans_1x1pt_US-NR1_ens_MIC_y1_2012.png}
     \caption{Response of control model states and fluxes to parameter perturbation across -1 to +1 range of parameter variation at Niwot Ridge.}
     \label{NR1 state}
  \end{figure}

   \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_STATE_1CLM50defpft_trans_1x1pt_US_Ha1_ens_MIC_y1_2012.png}
     \caption{Response of control model states and fluxes to parameter perturbation across -1 to +1 range of parameter variation at Harvard Forest}
     \label{HVF state}
  \end{figure}

 \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_FERT_1CLM50defpft_ndep_1x1pt_US_Ha1_ens_MIC_p1_2012.png}
     \caption{Influence of parametric variation (over the range tested: -1 to +1) on the influence of 15 years of Nitrogen fertilization (+5 kgN m$^{2}$ y$^{-1}$) at Harvard Forest}
     \label{HRV ndep}
  \end{figure}

   \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_FERT_1CLM50defpft_celev_1x1pt_US_Ha1_ens_MIC_p1_2012.png}
     \caption{Influence of parametric variation (over the range tested: -1 to +1) on the influence of 15 years of CO$_{2}$ fertilization (550ppm) at Harvard Forest}
     \label{HRV celev}
  \end{figure}

   \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_FERT_1CLM50defpft_ndep_1x1pt_Br-cax_ens_MIC_p1_2012.png}
     \caption{Influence of parametric variation (over the range tested: -1 to +1) on the influence of 15 uears of Nitrogen fertilization (+5 kgN m$^{2}$ y$^{-1}$) at Caxiuana}
     \label{CAX ndep}
  \end{figure}

   \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_FERT_1CLM50defpft_celev_1x1pt_Br-cax_ens_MIC_p1_2012.png}
     \caption{Influence of parametric variation (over the range tested: -1 to +1) on the influence of 15 years of CO$_{2}$ fertilization (550ppm) at Caxiuana }
     \label{CAX celev}
  \end{figure}

   \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth,left]{matlab/figures/NOVc_FERT_1CLM50defpft_ndep_1x1pt_US-Me2_ens_MIC_p1_2012.png}
     \caption{Influence of parametric variation (over the range tested: -1 to +1) on the influence of 15 years of Nitrogen fertilization (+5 kgN m$^{2}$ y$^{-1}$) at Metolius Forest}
     \label{MET ndep}
  \end{figure}

   \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_FERT_1CLM50defpft_celev_1x1pt_US-Me2_ens_MIC_p1_2012.png}
     \caption{Influence of parametric variation (over the range tested: -1 to +1) on the influence of 15 years of CO$_{2}$ fertilization (550ppm) at Metolius Forest}
     \label{MET celev}
  \end{figure}

   \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_FERT_1CLM50defpft_ndep_1x1pt_US-NR1_ens_MIC_p1_2012.png}
     \caption{Influence of parametric variation (over the range tested: -1 to +1) on the influence of 15 years of Nitrogen fertilization (+5 kgN m$^{2}$ y$^{-1}$) at Niwot Ridge}
     \label{NR1 ndep}
  \end{figure}

   \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_FERT_1CLM50defpft_celev_1x1pt_US-NR1_ens_MIC_p1_2012.png}
     \caption{Influence of parametric variation (over the range tested: -1 to +1) on the influence of 15 years of CO$_{2}$ fertilization (550ppm) at Niwot Ridge}
     \label{NR1 celev}
  \end{figure}
